PANCHANGE_data_preprocessing

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
added total disorder count and comorbidity count

glad.mhd.raw.id %>%
  freq(personality_cluster_a)
```

@@

glad.mhd.raw.id %>%
  freq(personality_cluster_b)
```

@@

glad.mhd.raw.id %>%
  freq(personality_cluster_c)
```

@@

glad.mhd.raw.id %>%
  freq(control)
```

>>>>

glad.mhd.raw.id %>%
  freq(personality_cluster_a,
       cumul = F)
```

@@

glad.mhd.raw.id %>%
  freq(personality_cluster_b,
       cumul = F)
```

@@

glad.mhd.raw.id %>%
  freq(personality_cluster_c,
       cumul = F)
```

@@

glad.mhd.raw.id %>%
  freq(control,
       cumul = F)
```

Total disorder count
```{r disorders_total_count}
disorder_columns <- c(
    "depressive_disorders_numeric",
    "anxiety_disorders_numeric",
    "eating_disorders_numeric",
    "obsessive_compulsive_disorders_numeric",
    "psychotic_disorders_numeric",
    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
    "mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric",
    "mhd.attention_deficit_hyperactivity_disorder_numeric",
    "mhd.personality_disorder_numeric"
)

glad.mhd.raw.id <- glad.mhd.raw.id %>%
  select(all_of(disorder_columns)) %>%
  mutate(
    disorders_total_count =
      rowSums(.)
  )

glad.mhd.raw.id %>%
  freq(disorders_total_count,
       cumul = F)
```

Comorbidity count
```{r}
glad.mhd.raw.id <- glad.mhd.raw.id %>%
  mutate(
    comorbidity_total_count = 
      case_when(
        disorders_total_count == 1 ~ 0,
        disorders_total_count > 1 ~ disorders_total_count - 1
  )
  )

glad.mhd.raw.id %>%
  freq(comorbidity_total_count,
       cumul = F)
```
